---
title: "p8105_hw5_wch2124"
output: html_document
date: '2023-11-13'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## problem 1 (0 points)
```{r}
## solution reviewed in class 
```

## problem 2 

```{r}
## load packages 
library(tidyverse)
library(rvest)
```

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

```{r}
##Start with a dataframe containing all file names; the list.files function will help

long_data = list.files("./data", pattern = ".csv", all.files = FALSE, 
full.names = FALSE)

#long_data
```

```{r}
## Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe and Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

tidy_data = data.frame(participants = long_data) |> 
  mutate(file_contents = map(participants, ~read.csv(file.path("./data", .)))) |>  
  separate(participants, into = c("control", "subject_id")) |>  
  unnest(file_contents) |> 
  mutate(control = recode(control, `con` = "control", `exp` = "experiment")) |>
  pivot_longer(week_1:week_8,
               names_to = "week",
               names_prefix = "week_",
               values_to = "observation")
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups:

```{r}
tidy_data |> 
  ggplot(aes(x = week, y = observation)) +
  geom_line(aes(group = subject_id, color = subject_id)) +
  labs(
    title = "Observations on Subjects Over Time",
    x = "Week",
    y = "Observations") + facet_grid(. ~ control)

## insert description here 
```

## problem 3 

First set the following design elements:

```{r}
set.seed(12345)
```

Set μ=0, Generate 5000 datasets from the model:

```{r}
sim_data_func = function(mu) {
  sim_data = tibble(rnorm(n = 30, mean = mu, sd = 5))
  
  sim_data |> 
    t.test() |> 
    broom::tidy() |> 
    select(estimate, p.value)

}

sim_results = 
  expand_grid(
    mu = 0,
    iter = 1:5000) |> 
  mutate(estimate_df = map(mu, sim_data_func)) |> 
  unnest(estimate_df)
## should we make a table of these values? 
```

Repeat the above for μ={1,2,3,4,5,6}:

```{r}
sim_results2 =
  expand_grid(
    mu = 1:6,
    iter = 1:5000) |> 
  mutate(estimate_df = map(mu, sim_data_func)) |> 
  unnest(estimate_df)
```

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power:

```{r}
sim_results2 |> 
  filter(p.value < 0.05) |> 
  group_by(mu) |> 
  summarise(power = n()/5000) |> 
  ggplot(aes(x = mu, y = power)) +
  geom_point() + labs(title = "Association Between Effect Size and Power") +
  geom_smooth()  

## insert description here 
```

Make a plot showing the average estimate of μ̂ on the y axis and the true value of μ on the x axis:

```{r}
sim_results2 |> 
  group_by(mu) |> 
  summarise(mu_estimate = mean(estimate)) |> 
  ggplot(aes(x = mu, y = mu_estimate)) +
  geom_point() + labs(title = "Comparing Estimates of Mu") +
  geom_smooth()  
  
```

Make a second plot the average estimate of μ̂ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis.

```{r}

sim_results2 |> 
  group_by(mu) |> 
  filter(p.value < 0.05) |> 
  summarise(mu_estimate = mean(estimate)) |> 
  ggplot(aes(x = mu, y = mu_estimate)) +
  geom_point() + labs(title = "Average Estimate of mu in Samples Where the Null was Rejected") +
  geom_smooth()


## add description here 
```

